The \frb\ Campaign: Multi-Observatory Radio Burst and Implications for the FRB Population

### 2017-02-06 repeater-vladata.tex
figure changed to energy dist

We visualize and model the burst energy distribution in two ways. First, the top panel of Figure \ref{fig:lumd} shows the \emph{cumulative} energy distribution and its best-fit powerlaw index of --0.6. Second, we use probabilistic modeling to the energies to quantify it directly. We model the energy distribution as a Poisson probability with rate function $\lambda=a\ E^\alpha$. Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts. The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{luminosity_cdisn}

\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{\emph{Top:} Cumulative energy distribution with powerlaw fit for the nine VLA bursts from \frb. \emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution. The powerlaw is referenced to $L=3\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}

>>>>

We visualize perform a simple modeling the burst energy distribution distribution and cumulative distribution in Figure \ref{fig:ed}.
The energy distribution powerlaw index is --0.5, while its cumulative energy distribution powerlaw index is --0.6.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{energy_disn}
\caption{The \frb\ burst energy distribution and cumulative distributino with powerlaw fits \label{fig:ed}}
\end{center}
\end{figure}
